\bf Supplementary Material to\\ ``Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test''

### 2025-10-08 manuscript/manuscript.tex
figures fixed

To evaluate the finite--sample impact, we compared the two corrections
through additional simulations; see results in Section~2 in the
Supplement.  Across all sample sizes and dependence
levels considered, the empirical sizes and powers were nearly identical.
This finding supports the theoretical argument that the circular block
bootstrap already captures the leading effects of serial correlation,
leaving little residual bias for the expectation centering to remove.
The comparable results of $K_n(x)$ and $C_n(x)$ suggest that the choice
between them is largely immaterial in practice.  We therefore retain
$K_n(x)$ for theoretical completeness and consistency of presentation,
while acknowledging that either correction performs similarly in finite
samples.

@@

Figure~\ref{fig:rr} displays the empirical power curve of the test at
significance level 0.05 as the lag-1 Kendall's~$\tau$ increases from
$-0.5$ to $0.5$. We omitted $-0.75$ and 0.75 from this study because we already
found that our method doesn't work under the null hypothesis for such high
dependence levels under the sample sizes considered. It appears that the
rejection rate seems to decline as $\tau$
increases. Rejection rates are negatively affected by positive serial
dependence, but they do not seem to be affected by negative serial dependencies
of the same strength.
Using $n \geq 400$ seems to be good enough
if $\tau < 0.5$, but using a $n \geq 800$ will result in
\jy{This inequality does not make sense.}
rejection rates close to 1 for $0.5 < \tau < 0.5$. 
Results for $n \geq 400$
do not appear to be to different when comparing gamma and normal
margins, indicating that the method is robust to the marginal distribution.
The rejection rates for $n = 800$ are very
high (almost 1), indicating that under $H_A$, the test is very powerful
when a large enough sample size is used.

@@

The KS test remains a crucial tool for researchers across diverse fields,
enabling critical assessments of population distributions. We introduced a
NPBB variant of the KS test tailored for data with
serial dependencies, which eliminates the need for explicit modeling serial
dependence in addition to parameter specification within the hypothesized
distribution. Our simulations have demonstrated that, given
sufficiently large samples of time series data and moderate serial dependencies,
the test maintains its size under the null hypothesis and have considerable
power in detecting deviations from the hypothesized marginal distribution. The
method's performance improves as the strength of temporal dependence decreases
or the sample size increases. For moderate serial dependence levels in practice,
the test can be recommended for sample size~$n = 400$ or higher.
Overall, the test provides an analog of the bias-corrected NPB KS test of
\citet{babu2004goodness} in the context of stationary time
series with unspecified serial dependence. Compared to the SPB method
of \citet{zeimbekakis2024misuses}, which requires a working dependence model, it
is reliable with no need to worry about whether the working dependence
model approximates the true dependence model.

@@

***Section here describing practical conclusions/recommendations for
bias correction***

>>>>

To evaluate the finite--sample impact, we compared the two corrections
through additional simulations; see results in Section~1 in the
Supplement.  Across all sample sizes and dependence
levels considered, the empirical sizes and powers were nearly identical.
This finding supports the theoretical argument that the circular block
bootstrap already captures the leading effects of serial correlation,
leaving little residual bias for the expectation centering to remove.
The comparable results of $K_n(x)$ and $C_n(x)$ suggest that the choice
between them is largely immaterial in practice.  We therefore retain
$K_n(x)$ for theoretical completeness and consistency of presentation,
while acknowledging that either correction performs similarly in finite
samples.

@@

Figure~\ref{fig:rr} displays the empirical power curve of the test at
significance level 0.05 as the lag-1 Kendall's~$\tau$ increases from
$-0.5$ to $0.5$. We omitted $-0.75$ and 0.75 from this study because we already
found that our method doesn't work under the null hypothesis for such high
dependence levels under the sample sizes considered. It appears that the
rejection rate seems to decline as $\tau$
increases. Rejection rates are negatively affected by positive serial
dependence, but they do not seem to be affected by negative serial dependencies
of the same strength.
Using $n \geq 400$ seems to be good enough
if $\tau < 0.5$, but using a $n \geq 800$ will result in
rejection rates close to 1 for $-0.5 < \tau < 0.5$. 
Results for $n \geq 400$
do not appear to be to different when comparing gamma and normal
margins, indicating that the method is robust to the marginal distribution.
The rejection rates for $n = 800$ are very
high (almost 1), indicating that under $H_A$, the test is very powerful
when a large enough sample size is used.

@@

The KS test remains a crucial tool for researchers across diverse fields,
enabling critical assessments of population distributions. We introduced a
NPBB variant of the KS test tailored for data with
serial dependencies, which eliminates the need for explicit modeling serial
dependence in addition to parameter specification within the hypothesized
distribution. Our simulations have demonstrated that, given
sufficiently large samples of time series data and moderate serial dependencies,
the test maintains its size under the null hypothesis and have considerable
power in detecting deviations from the hypothesized marginal distribution. The
method's performance improves as the strength of temporal dependence decreases
or the sample size increases. For moderate serial dependence levels in practice,
the test can be recommended for sample size~$n = 400$ or higher.
Overall, the test provides an analog of the bias-corrected NPB KS test of
\citet{babu2004goodness} in the context of stationary time
series with unspecified serial dependence. Compared to the SPB method
of \citet{zeimbekakis2024misuses}, which requires a working dependence model, it
is reliable with no need to worry about whether the working dependence
model approximates the true dependence model. We note that while the
expectation centering in our paper removes a minor bias term, it is identical
in asymptotic performance to \citet{babu2004goodness}'s correction under 
short--range dependence.

@@

### 2025-10-08 manuscript/supplement.tex
figures fixed

Based on Figures~\ref{fig:qq_n_C_n, fig:qq_g_C_n, fig:rr_C_n}, the empirical performance is very similar under either choice of bias correction term. For practical applications, we recommend.....

@@

We evaluated the size and power performance of the NPBB test under automatic
block length selection. The size performance is shown
in Figures~\ref{fig:alt_qq_n} and \ref{fig:alt_qq_g}, which display Q-Q plots
of the $p$-values under the null for Normal and Gamma margins, respectively.
Recall from Figures~\ref{fig:qq_n} and \ref{fig:qq_g} that the cubic root 
setting holds its size quite well with small $n$ for $|\tau| \leq 0.25$,
whereas achieving nominal size for $|\tau| \geq 0.5$ require
$n > 200$, and for $|\tau| \geq 0.75$ require $n > 800$. The automatic
selection shows similar limitations for $|\tau| > 0.5$, where it does
not hold its size. Moreover, deviations from the diagonal line appear
larger for negative $\tau$, likely due to the high proportion of
occurrence of overly large block sizes. For example, while the cubic
root setting held its size well at $\tau = -0.25$ with small~$n$, the
automatic selection does not. At the same time, under $\tau = 0$ or
$\tau = 0.25$, the method with block size selected by
\citep{politis2004automatic} maintains reasonable size for moderately
positively dependent series.

Figure~\ref{fig:alt_rr} shows the power results under automatic selection.
When compared to Figure~\ref{fig:rr}, the two settings exhibit similar power
for $|\tau| \leq 0.5$, with the automatic selection sometimes yielding higher
rejection rates, particularly for smaller negatively dependent samples.
Overall, while the automatic selection from \citep{politis2004automatic}
performs reasonably well in certain settings, we recommend caution when using
it under negative~$\tau$ and smaller sample sizes, where maintaining nominal
size may be more difficult. In such cases, it may be sensible to apply a more
restrictive rule when setting the final block size---for example, using
$\min \{\sqrt{n}, \hat{l}\}$.

>>>>

Based on Figures~\ref{fig:qq_n_C_n, fig:qq_g_C_n, fig:rr_C_n}, 
the empirical performance in both size and power analysis is very similar under 
either choice of bias correction 
term. This suggests that the circular block bootstrap already corrects for
much of the temporal dependence, and that the choice of centering
has a very small effect on residual bias. Using $C_n(x)$ has the advantage
of requiring slightly less computation, but we 
still recommend $K_n(x)$ for its theoretical qualities, but acknowledge that
performance may be indistinguishable in practical application, especially
with large sample size and dependence that decays rapidly.

@@

We evaluated the size and power performance of the NPBB test under automatic
block length selection. The size performance is shown
in Figures~\ref{fig:alt_qq_n} and \ref{fig:alt_qq_g}, which display Q-Q plots
of the $p$-values under the null for Normal and Gamma margins, respectively.
Recall from the Q-Q plots in the main paper that the cubic root 
setting holds its size quite well with small $n$ for $|\tau| \leq 0.25$,
whereas achieving nominal size for $|\tau| \geq 0.5$ require
$n > 200$, and for $|\tau| \geq 0.75$ require $n > 800$. The automatic
selection shows similar limitations for $|\tau| > 0.5$, where it does
not hold its size. Moreover, deviations from the diagonal line appear
larger for negative $\tau$, likely due to the high proportion of
occurrence of overly large block sizes. For example, while the cubic
root setting held its size well at $\tau = -0.25$ with small~$n$, the
automatic selection does not. At the same time, under $\tau = 0$ or
$\tau = 0.25$, the method with block size selected by
\citep{politis2004automatic} maintains reasonable size for moderately
positively dependent series.

Figure~\ref{fig:alt_rr} shows the power results under automatic selection.
When compared to the power curve in the main paper, the two settings exhibit 
similar power
for $|\tau| \leq 0.5$, with the automatic selection sometimes yielding higher
rejection rates, particularly for smaller negatively dependent samples.
Overall, while the automatic selection from \citep{politis2004automatic}
performs reasonably well in certain settings, we recommend caution when using
it under negative~$\tau$ and smaller sample sizes, where maintaining nominal
size may be more difficult. In such cases, it may be sensible to apply a more
restrictive rule when setting the final block size---for example, using
$\min \{\sqrt{n}, \hat{l}\}$.
